% Simple Resume Template with Jinja2 Placeholders
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\begin{document}

% Header
\begin{center}
    {\huge\textbf{Shalom DOSSEH}} \\
    \vspace{2mm}
    dosseh.contact@gmail.com $|$
    Github: AnalyticAce $|$
    LinkedIn: DOSSEH Shalom
\end{center}


% Profile
\section*{Profile}
Data Professional with a strong foundation in Python programming and a genuine interest in generative AI technologies. Experienced in developing AI-driven applications and collaborating with cross-functional teams to deliver innovative solutions.



% Experience
\section*{Work Experience}

\textbf{Data Science \& Analytics - Internship} \hfill Jul. 2024 -- Apr. 2025 \\
\textit{Gozem - Africa's Super App} \\
\begin{itemize}
    
    \item Partnered with Gozem Money leadership to understand data requirements for the pre-launch phase of a new fintech vertical, including data extraction and analysis across large-scale financial datasets for financial forecasting and transaction analytics.
    
    \item Utilized Python (Pandas, Scikit-learn), SQL, and Looker Studio to generate actionable insights and align business needs with technical solutions.
    
    \item Leveraged SQL and Astro Airflow to design and implement real-time transaction monitoring for \textbf{8,000,000+} monthly transactions to detect and prevent fraud, money laundering, and terrorist financing activities.
    
    \item Collaborated with the data engineering team to gather, structure, and integrate data from multiple sources into a centralized analytics repository, enabling a unified view of key product insights.
    
\end{itemize}

\textbf{Data Analyst (Ride-hailing) - Internship} \hfill Sep. 2023 -- Jan. 2024 \\
\textit{Gozem - Africa's Super App} \\
\begin{itemize}
    
    \item Executed \textbf{65}\%+ of the squad’s quarterly tasks, completing \textbf{92}\% of high-priority deliverables efficiently.
    
    \item Investigated transaction data, detecting and dismantling fraudulent schemes, leading to millions in recovered revenue.
    
    \item Performed data integrity checks, identifying and resolving anomalies to maintain accurate reporting.
    
    \item Automated routine reporting and analytics tasks, improving efficiency and precision in data insights.
    
\end{itemize}




% Projects
\section*{Projects}

\textbf{MyResumo} \\
\begin{itemize}
    
    \item Built an AI-backed resume generator designed to tailor your resume and skills based on a given job description.
    
    \item Leveraged the latest advancements in AI to provide an ATS-friendly resume.
    
    
    \item Innovative tool that helps users create optimized resumes for job applications.
    
\end{itemize}

\textbf{MyTorch} \\
\begin{itemize}
    
    \item Developed a neural network-based chessboard analyzer from scratch without deep learning libraries.
    
    \item Trained models on FEN notation to classify six game states.
    
    
    \item Achieved \textbf{90}\% accuracy in binary classification and \textbf{60}-\textbf{70}\% in multi-class tasks.
    
\end{itemize}

\textbf{Gomoku AI} \\
\begin{itemize}
    
    \item Developed a high-performance Gomoku AI bot using Min-Max with Alpha-Beta pruning and heuristic scoring.
    
    \item Designed to compete with GomokuCup AI bots, ensuring efficiency under computational constraints.
    
    
    \item Optimized decision-making for the Gomoku game.
    
\end{itemize}

\textbf{PyDepViz} \\
\begin{itemize}
    
    \item A Python-native dependency graph visualizer designed to simplify dependency management in Python projects.
    
    \item Helps developers visualize and resolve dependency deadlocks efficiently.
    
    
    \item Tool that aids in managing Python project dependencies.
    
\end{itemize}




% Education
\section*{Education}

\textbf{EPITECH - European Institute of Technology} \hfill Oct. 2022 -- Present \\
\textit{Bachelor's degree, Innovation and Information Technology} \\

Cultivated robust skills across various domains of computer science, completing nearly 130 projects and mini-projects. Relevant Courses: Computer Numerical Analysis, Artificial Intelligence, Advanced DevOps, Advanced C++.





% Skills
\section*{Skills}

\textbf{Technical Skills:} Python, SQL, Pandas, NumPy, Scikit-Learn, Looker Studio, Excel, GCP, Azure, MongoDB, Docker, Jenkins, Ansible, Apache Airflow, Git Source Control, Github action, Linux \\


\textbf{Soft Skills:} Adaptability, Coachable, Problem-Solving, Decision-Making, Effective communication, Active listening




% Certifications
\section*{Certifications}
\begin{itemize}
    
    \item Career Essentials in GitHub Professional Certificate (Github, Expected Feb. 2025)
    
    \item Data Scientist Certification (Datacamp, Expected Jul. 2025)
    
    \item AI Engineer for Data Scientists Associate Certification (Datacamp, Expected Sep. 2025)
    
    \item Certified Associate in Project Management (CAPM) (PMI, Expected Sep. 2025)
    
\end{itemize}


\end{document}