%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Shalom DOSSEH} \\ \vspace{1pt}
    \href{mailto:dosseh.contact@gmail.com}{\underline{dosseh.contact@gmail.com}} $|$ 
    \href{https://github.com/AnalyticAce}{\underline{Github: AnalyticAce}} $|$
    \href{https://www.linkedin.com/in/shalom-dosseh-4a484a262/}{\underline{LinkedIn: DOSSEH Shalom}}
\end{center}


%-----------EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Gozem - Africa's Super App}{Cotonou, Benin}
      {Data Science \& Analytics - Internship}{July 2024 -- April 2025}
      \resumeItemListStart
        \resumeItem{Partnered with Gozem Money leadership to understand data requirements for the pre-launch phase of a new fintech vertical, including data extraction, and analysis across large-scale financial datasets for financial forecasting, and transaction analytics.}
        \resumeItem{Utilized Python (Pandas, Scikit-learn), SQL, and Looker Studio to generate actionable insights and align business needs with technical solutions.}
        \resumeItem{Leveraged SQL and Astro Airflow to design and implement real-time transaction monitoring \textbf{8,000,000+ monthly transactions}, to detect and prevent fraud, money laundering, and terrorist financing activities, leveraging rule-based and anomaly detection models.}
        \resumeItem{Collaborated with the data engineering team to gather, structure, and integrate data from multiple sources (App Stores, Firebase, Data Warehouse) into a centralized analytics repository, enabling a unified view of key product insights.}
        \resumeItem{Worked closely with the Head of Data to define core KPIs for tracking app performance across digital storefronts, in-app engagement, and crash analytics, equipping product managers with data-driven insights to optimize user experience, and app store rankings.}
      \resumeItemListEnd
    
    \resumeSubheading
      {Gozem - Africa's Super App}{Cotonou, Benin}
      {Data Analyst (Ride-hailing) - Internship}{Sept. 2023 -- Jan. 2024}
      \resumeItemListStart
        \resumeItem{Executed \textbf{65\%+ of the squad's quarterly tasks}, completing \textbf{92\% of high-priority} deliverables efficiently.}
        \resumeItem{Investigated transaction data, detecting and dismantling fraudulent schemes, leading to \textbf{millions in recovered revenue.}}
        \resumeItem{Performed data integrity checks, identifying and resolving anomalies to maintain accurate reporting.}
        \resumeItem{Automated routine reporting and analytics tasks, improving efficiency and precision in data insights.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{MyResumo} $|$ \emph{Python, FastAPI, Natural Language Processing, Prompt Engineering}}{} 
          \resumeItemListStart
            \resumeItem{Built an \textbf{AI-backed resume generator} designed to tailor your resume and skills based on a given job description. This innovative tool leverages the latest advancements in AI to provide you with an \textbf{ATS friendly resume}.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{MyTorch} $|$ \emph{Computational Analysis, Azure}}{}
          \resumeItemListStart
            \resumeItem{Developed a neural network-based chessboard analyzer from scratch without deep learning libraries. Trained models on FEN notation to classify six game states, achieving \textbf{90\% accuracy in binary classification} and \textbf{60-70\% in multi-class tasks}.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Gomoku AI} $|$ \emph{Genetic Algorithm}}{}
          \resumeItemListStart
            \resumeItem{Developed a \textbf{high-performance Gomoku AI} bot using \textbf{Min-Max with Alpha-Beta} pruning and heuristic scoring to optimize decision-making. Designed to compete with GomokuCup AI bots, ensuring efficiency under computational constraints.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{PyDepViz} $|$ \emph{Package, Git Action}}{}
          \resumeItemListStart
            \resumeItem{A \textbf{Python-native dependency graph visualizer} designed to simplify dependency management in Python projects. It helps developers visualize and resolve dependency deadlocks efficiently.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {EPITECH - European Institute of Technology}{Cotonou, Benin}
      {Bachelor's degree, Innovation and Information Technology}{Oct. 2022 -- June 2025}
      \resumeItemListStart
        \resumeItem{I have cultivated robust skills across various domains of computer science, completing nearly 130 projects and mini-projects.}
        \resumeItem{Relevant Courses: Computer Numerical Analysis, Artificial Intelligence, Advanced DevOps, Advanced C++}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: English (Proficient), French (Native)} \\
     \textbf{Programming}{: Python, SQL, Bash} \\
     \textbf{Soft Skills}{: Adaptability, Coachable, Problem-Solving, Decision-Making, Effective communication, Active listening} \\
     \textbf{Data Tools}{: Pandas, NumPy, Scikit-Learn, FastAPI, Looker Studio, Excel} \\
     \textbf{Cloud \& DevOps}{: GCP, Azure, MongoDB, Docker, Jenkins, Ansible, Apache Airflow, Git Source Control, Github action, Linux}
    }}
 \end{itemize}

%-----------LEADERSHIP-----------
\section{Leadership \& Community Involvement}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Technical Workshop Facilitator}{Innovation Hub at Epitech}
      {}{March 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Hosted Python, DevOps, and AI workshops, mentoring students in technical fields.}
        \resumeItem{Partnered with industry professionals to deliver hands-on training sessions.}
      \resumeItemListEnd
    
    \resumeSubheading
      {Lead Project Manager}{Epitech's Student Bureau}
      {}{March 2024 -- Present}
      \resumeItemListStart
        \resumeItem{Led a team of 3 project managers, overseeing 30+ initiatives within time and budget constraints.}
        \resumeItem{Developed planning \& tracking tools to optimize project execution.}
      \resumeItemListEnd
    
    \resumeSubheading
      {Event Manager \& Core Member}{Google Developer Students Club}
      {}{June 2023 -- July 2024}
      \resumeItemListStart
        \resumeItem{Organized tech events, hackathons, and networking sessions to engage student developers.}
        \resumeItem{Drove community initiatives to enhance learning in AI \& Google Cloud Technologies.}
      \resumeItemListEnd
    
    \resumeSubheading
      {Social Data Analyst}{AFRIK EDUTECH - EPITECH X IMPACT}
      {}{Dec 2023 -- Dec 2024}
      \resumeItemListStart
        \resumeItem{Conducted impact analysis \& forecasting, guiding leadership decisions on program effectiveness.}
        \resumeItem{Collected \& cleaned large-scale datasets for resource optimization.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------
\section{Certifications}
  \resumeSubHeadingListStart
    \resumeItem{Career Essentials in GitHub Professional Certificate (Github, Completed February 2025)}
    \resumeItem{Data Scientist Certification (Datacamp, Expected July 2025)}
    \resumeItem{AI Engineer for Data Scientists Associate Certification (Datacamp, Expected Sept 2025)}
    \resumeItem{Certified Associate in Project Management (CAPM) (PMI, Expected Sept 2025)}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}